Relocating a Cluster of Earthquakes Using a Single Seismic Station

### 2012-12-21 paper2/paper2.tex
commiting final changes prior to paper submission

% Figure 5
\begin{figure}
\noindent\includegraphics[width =
20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
\caption{Map showing location of the Calaveras cluster (white star)
and 805 seismic stations (black triangles).}
\label{fig:-eqopti-California-Calaveras}
\end{figure}

@@

% Now we have the SVD version
\begin{figure*}
\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
\caption{Example 5 - Comparison of relative earthquake locations
using three different methods: catalogue location (column 1), CWI
(column 2) and hypoDD (column 3). Note that in the case of the
hypoDD and CWI inversions we consider only the 68 earthquakes in
black, the gray catalogue locations for the remaining 240 (308-68)
earthquakes are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}
%%=======================================================================================

@@

%Figure 8
\begin{figure*}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
\caption{Example 6 - CWI relative locations with reduced stations.}
\label{fig-CWIreducesstats}
\end{figure*}

@@

% This is the version using hypoDD with SVD
\begin{figure*}
\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
\caption{Example 6 - HypoDD (SVD) relative locations with reduced
stations.} \label{fig-HYPODDreducesstats}
\end{figure*}
%%=========================================================================

@@

% This is the version using hypoDD with SVD
\begin{figure}
\noindent\includegraphics[width =
20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
Number of constrainable events $nE$ in the CWI and hypoDD inversions
as a function of the stations considered (top). Mean (middle) and
maximum (bottom) of the difference computed between the reduced
station inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. } \label{fig-statremoval_summarystats}
\end{figure}

@@

% This is the version using hypoDD with SVD
\begin{figure}
\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
locations using data form all stations (left) and 5 stations
(right).} \label{fig-68Calaverasevents_ttandcoda1}
\end{figure}

@@

\begin{figure}
%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
\caption{Cumulative number of aftershocks for the
Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
using equation (\ref{eq:CumOmori}). The leftmost gray, middle black
and rightmost gray lines signify aftershocks occurring before,
during and after the deployment of a pseudo temporary array
installed 4 days after the main shock and left for 150 days. A
temporary deployment of this kind will record roughly 50\% of the
aftershocks in the 1000 days following the mainshock. }
\label{fig:Omorifigure}
\end{figure}

@@

% This is the version using hypoDD with SVD
\begin{figure}
\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
\caption{Example 8 - Mimicking the deployment of a temporary network
by ignoring data from all but station CCO for 50\% (or 34) of the
events. Relative locations are shown for the combined CWI and travel
time inversion (left) and the inversion with travel times only
(right) Only by combining the data is it possible to locate all 68
events. Furthermore, combining the data leads to a solution more
consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
\label{fig-68Calaverasevents_ttsubsetandcoda1}
\end{figure}
%%=========================================================================

>>>>

% Figure 5
\begin{figure}
%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
\noindent\includegraphics[width=20pc]{Figure5.eps} \caption{Map
showing location of the Calaveras cluster (white star) and 805
seismic stations (black triangles).}
\label{fig:-eqopti-California-Calaveras}
\end{figure}

@@

% Now we have the SVD version
\begin{figure*}
%\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
\includegraphics{Figure6_bw.eps}
\caption{Example 5 - Comparison of relative earthquake locations
using three different methods: catalogue location (column 1), CWI
(column 2) and hypoDD (column 3). Note that in the case of the
hypoDD and CWI inversions we consider only the 68 earthquakes in
black, the gray catalogue locations for the remaining 240 (308-68)
earthquakes are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}
%%=======================================================================================

@@

%Figure 8
\begin{figure*}
%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
\caption{Example 6 - CWI relative locations with reduced stations.}
\label{fig-CWIreducesstats}
\end{figure*}

@@

% This is the version using hypoDD with SVD
\begin{figure*}
%\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
\includegraphics[height = 25pc]{Figure9_bw.eps}
\caption{Example 6 - HypoDD (SVD) relative locations with reduced
stations.} \label{fig-HYPODDreducesstats}
\end{figure*}
%%=========================================================================

@@

% This is the version using hypoDD with SVD
\begin{figure}
%\noindent\includegraphics[width=20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
\noindent\includegraphics[width=20pc]{Figure10_c.eps}
\caption{Example 6 - Number of constrainable events $nE$ in the CWI
and hypoDD inversions as a function of the stations considered
(top). Mean (middle) and maximum (bottom) of the difference computed
between the reduced station inversion results (CWI and hypoDD) and
the complete hypoDD locations for all 308 events. }
\label{fig-statremoval_summarystats}
\end{figure}

@@

% This is the version using hypoDD with SVD
\begin{figure}
%\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
\includegraphics{Figure11_bw.eps}
\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
locations using data form all stations (left) and 5 stations
(right).} \label{fig-68Calaverasevents_ttandcoda1}
\end{figure}

@@

\begin{figure}
%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
\caption{Cumulative number of aftershocks for the
Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
using equation (\ref{eq:CumOmori}). The leftmost red, middle blue
and rightmost red lines signify aftershocks occurring before, during
and after the deployment of a pseudo temporary array installed 4
days after the main shock and left for 150 days. A temporary
deployment of this kind will record roughly 50\% of the aftershocks
in the 1000 days following the mainshock. } \label{fig:Omorifigure}
\end{figure}

@@

% This is the version using hypoDD with SVD
\begin{figure}
%\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
\includegraphics{Figure13_bw.eps}
\caption{Example 8 - Mimicking the deployment of a temporary network
by ignoring data from all but station CCO for 50\% (or 34) of the
events. Relative locations are shown for the combined CWI and travel
time inversion (left) and the inversion with travel times only
(right). Only by combining the data is it possible to locate all 68
events. Furthermore, combining the data leads to a solution more
consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
\label{fig-68Calaverasevents_ttsubsetandcoda1}
\end{figure}
%%=========================================================================
